---
title: "Shelby Bachman's CV"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [cv.css]
    number_sections: false
links-to-footnotes: false
---

```{r setup, include=FALSE}

library(here)
library(data.table)
library(tidyverse)
library(lubridate)
library(knitr)

opts_chunk$set(echo = FALSE, 
               message = FALSE,
               warning = FALSE)
options(knitr.kable.NA = '')

# cv entries
cv_entries <- fread(here("data", "cv_entries.csv"))
cv_entries$bold[is.na(cv_entries$bold)] <- 0

# publications
pubs <- fread(here('data', 'pubs.csv'), 
              na.strings = '')

# presentations
pres <- read.csv(here('data', 'presentations.csv'))

# courses
courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))

```


```{r}
PDF <- FALSE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
if(PDF) {
  header <- '
  View online
  <a href="https://shelbybachman.github.io/bachman-cv" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a>
  '
} else {
  header <- '
  Download PDF
  <a href="https://github.com/shelbybachman/bachman-cv/raw/master/cv.pdf" class="icon-block">
      <i class="fas fafooter fa-download"></i>
  </a>
  '
}
```

<div class = "download">

```{r results = "asis"}
cat(header)
```

</div>

<div class = "footer",>
  <a href="https://github.com/shelbybachman/" class="icon-block">
      <i class="fab fafooter fa-github"></i>
  </a> |
  
  <a href="mailto:sbachman@usc.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"></i>
  </a> |
  
  <a href="https://shelbybachman.github.io" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a> |
  
  <a href="(https://orcid.org/0000-0002-4460-4661" class="icon-block">
      <i class="fab fafooter fa-orcid"></i>
  </a>
  
</div>


<div id = "block_container">

<div class = "first", id="bloc1">Shelby</div>  
<div class = "last", id="bloc2">Bachman</div>

</div>

<div id = "position", class = "position">
PhD Candidate
</div>

<div class="grid-container">

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

## Education {.education .nohead}

```{r}

cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = ifelse(bold == 1, paste0("<span style= 'font-weight: 500'>", what, "</span>"),
                       ifelse(bold == 0, what, NA))) %>%
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what),
         year_end = ifelse(is.na(year_end), '', year_end)
         ) %>% 
  mutate(year = str_c(year_begin, " - ", year_end)) %>% 
  select(year, what) %>% 
  kable()

```

## Research experience {.research .nohead}

```{r}

cv_entries %>% 
  filter(type == 'research') %>% 
  mutate(what = ifelse(bold == 1, paste0("<span style= 'font-weight: 500'>", what, "</span>"),
                       ifelse(bold == 0, what, NA))) %>%
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " - ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()

```

<br class="pageBreak"/>

## Awards & Funding {.award .nohead}

<div class="hangingindent">

```{r}

cv_entries %>%
  filter(type == "award") %>%
  mutate(year_end = ifelse(is.na(year_end), '', paste(' - ', year_end, sep = '')),
         cite = paste0(what, " (", year_begin, year_end, "). ", 
                       ifelse(!is.na(additional_info), 
                              paste0(additional_info, "."),
                              "")
                       )
        ) %>%
  select(cite) %>%
  kable()

```

</div>

## Peer-Reviewed Publications {.prpa .nohead}

<div class = "inote">
Icons link to additional content  
</div>

```{r}

# custom function to format publication citations
make_cite_pub <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL, ...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
     pages <- paste0(pages,".") 
  }

  authors <- gsub(
    "Bachman SL\\.?",
    "<span style= 'font-weight: 500'>Bachman SL</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, "."),
        journal, 
        volume,
        pages, 
        doi)
}

# select only peer-reviewed publications
prp <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

# format citations
each_cite <- split(prp, seq_len(nrow(prp)))
empties <- map(each_cite, ~map_lgl(.x, is.na))
cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite_pub, .x)) 

# add icons if relevant links are available
fa_doc <- ifelse(
  !is.na(prp$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prp$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prp$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prp$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prp$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
#  group_by(year) %>%
#  mutate(count_within_year = 1:n()) %>% 
#  ungroup() %>% 
#  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
#  select(-count_within_year) %>%
  select(-year, -count)

kable(pubs_tbl)

```

## Manuscripts under review for publication {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "in-review") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 
  
  kable(submitted_tbl) 
}
```

</div>

## Conference presentations & other talks {.prpa .nohead}

<div class = "hangingindent">

```{r}

# custom function to format presentation citations
make_cite_pres <- function(type, authors,	date,	title,
                           conference = NULL, poster = NULL, conf_loc = NULL, annual_meeting = NULL, ...) {
  
  if(type == 'conference') {
    title <- paste0("*", title, "*")
       if(annual_meeting == 1) {
          conference <- paste0("Paper presented at the annual meeting of the ", 
                            conference, 
                            ', ', 
                            conf_loc,
                            '.', 
                            sep = '') 
      }
      else if (annual_meeting == 0) {
        conference <- paste0("Paper presented at the ", 
                             conference, 
                             ', ', 
                             conf_loc,
                             '.', 
                             sep = '') 
      }
  } else if (type == 'talk') {
    title <- paste0("*", title, "*")
    conference <- paste0(conference, 
                         ', ', 
                         conf_loc, 
                         '.',
                         sep = '')
  }
  
  # make name bold
  authors <- gsub(
    "Bachman SL\\.?",
    "<span style= 'font-weight: 500'>Bachman SL</span>", 
    authors)
#  authors <- gsub(
#    "Bachman S\\.?",
#    "<span style= 'font-weight: 500'>Bachman S</span>", 
#    authors)

   
  paste(authors, 
        paste0("(", date, ")."), 
        paste0(title, "."),
        conference)
}

# select only conference presentations & other talks
talks <- pres %>%
  filter(type %in% c('conference', 'talk'))

# add icon if a link to slides is available
fa_pres <- ifelse(
  !is.na(talks$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         talks$slides_link, 
         ")"
         ),
  ""
  )

# format citations
each_cite <- split(talks, seq_len(nrow(talks)))
empties <- map(each_cite, ~map_lgl(.x, is.na))
cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite_pres, .x)) 

# create tibble with presentation entries
talks_tbl <- tibble(year = talks$date,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_pres)
)

# don't keep year or count 
talks_tbl <- talks_tbl %>% 
#  mutate(year = parse_number(year)) %>% 
#  group_by(year) %>%
#  mutate(count_within_year = 1:n()) %>% 
#  ungroup() %>% 
#  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
#  select(-count_within_year)
  select(-year, -count)

kable(talks_tbl)

```

</div>

## Poster presentations {.prpa .nohead}

<div class = "hangingindent">

```{r}

# custom function to format presentation citations
make_cite_poster <- function(type, authors,	date,	title,
                           conference = NULL, poster = NULL, conf_loc = NULL, annual_meeting = NULL, ...) {
  
  if(type == 'poster') {
    title <- paste0("*", title, "*")
       if(annual_meeting == 1) {
          conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference, 
                            ', ', 
                            conf_loc,
                            '.', 
                            sep = '') 
      }
      else if (annual_meeting == 0) {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                             ', ', 
                             conf_loc,
                             '.', 
                             sep = '') 
      }
  }
  
  # make name bold
  authors <- gsub(
    "Bachman SL\\.?",
    "<span style= 'font-weight: 500'>Bachman SL</span>", 
    authors)
#  authors <- gsub(
#    "Bachman S\\.?",
#    "<span style= 'font-weight: 500'>Bachman S</span>", 
#    authors)

  paste(authors, 
        paste0("(", date, ")."), 
        paste0(title, "."),
        conference)
}

# select only conference presentations & other talks
posters <- pres %>%
  filter(type == 'poster')

# add icon if a link to slides is available
fa_pres <- ifelse(
  !is.na(posters$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         posters$slides_link, 
         ")"
         ),
  ""
  )

# format citations
each_cite <- split(posters, seq_len(nrow(posters)))
empties <- map(each_cite, ~map_lgl(.x, is.na))
cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite_poster, .x)) 

# create tibble with presentation entries
poster_tbl <- tibble(year = posters$date,
                     count = paste0(seq(length(formatted_cites), 1), "."),
                     cites = paste(unlist(formatted_cites), 
                                   fa_pres)
)

# don't keep year or count 
poster_tbl <- poster_tbl %>% 
#  mutate(year = parse_number(year)) %>% 
#  group_by(year) %>%
#  mutate(count_within_year = 1:n()) %>% 
#  ungroup() %>% 
#  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
#  select(-count_within_year)
  select(-year, -count)

kable(poster_tbl)

```

</div>

## Teaching {.nohead .tch}

<div class = "inote">
Icons link to additional content  
</div>

```{r}
courses %>% 
  filter(type == "ds") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                         ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""), 
                         credits, " credit hours.",
                         fa_git, fa_web),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()

```

<br class="pageBreak"/>

## Academic service {.nohead}

I serve on the editorial review board for [Reading Research Quarterly](https://ila.onlinelibrary.wiley.com/journal/19362722) and have served as an ad hoc reviewer for the following journals:

<div class = "adhoc">

```{r}
reviewer <- cv_entries %>%
  filter(type == "peer-reviewer") %>%
  select(what) %>%
  mutate(index = c(rep(1, floor(nrow(.)/2)), 
                   rep(2, nrow(.) - floor(nrow(.)/2))
                   ))


jou1 <- reviewer$what[reviewer$index == 1]
jou2 <- reviewer$what[reviewer$index == 2]

if(length(jou1) < length(jou2)) {
  jou1 <- c(jou1, NA)
}
if(length(jou2) < length(jou1)) {
  jou2 <- c(jou2, NA)
}

data.frame(jou1, jou2) %>%
  kable()
```

</div>

## Statistical training {.nohead .extratrain}

<div class = "hangingindent">
```{r}
cv_entries %>% 
  filter(type == "extra-training") %>% 
  mutate(training = paste0(what, " (", year_end, "). ", where, "\\n")) %>% 
  select(training) %>% 
  kable()
```
<div/>

<!-- <br class="pageBreak"> -->

