---
title: "Shelby Bachman's CV"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [cv.css]
    number_sections: false
links-to-footnotes: false
---

```{r setup, include=FALSE}

library(here)
library(tidyverse)
library(lubridate)
library(knitr)

opts_chunk$set(echo = FALSE, 
               message = FALSE,
               warning = FALSE)
options(knitr.kable.NA = '')

# cv entries
cv_entries <- read.csv(here("data", "cv_entries.csv"))
cv_entries$bold[is.na(cv_entries$bold)] <- 0

# publications
pubs <- read.csv(here("data", "pubs.csv")) %>% 
  arrange(order) %>% 
  select(-order) %>%
  mutate(annual_meeting = as.logical(annual_meeting),
         poster = as.logical(poster))
pubs <- map_df(pubs, ~gsub("\\.$", "", .x))

# courses
courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))

```


```{r}
PDF <- FALSE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
if(PDF) {
  header <- '
  View online
  <a href="https://shelbybachman.github.io/bachman-cv" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a>
  '
} else {
  header <- '
  Download PDF
  <a href="https://github.com/shelbybachman/bachman-cv/raw/master/cv.pdf" class="icon-block">
      <i class="fas fafooter fa-download"></i>
  </a>
  '
}
```

<div class = "download">
```{r results = "asis"}
cat(header)
```

</div>

<div class = "footer",>
  <a href="https://github.com/shelbybachman/" class="icon-block">
      <i class="fab fafooter fa-github"></i>
  </a> |
  
  <a href="mailto:sbachman@usc.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"></i>
  </a> |
  
  <a href="https://shelbybachman.github.io" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a> |
  
  <a href="(https://orcid.org/0000-0002-4460-4661" class="icon-block">
      <i class="fab fafooter fa-orcid"></i>
  </a>
  
</div>


<div id = "block_container">

<div class = "first", id="bloc1">Shelby</div>  
<div class = "last", id="bloc2">Bachman</div>

</div>

<div id = "position", class = "position">
PhD Candidate
</div>

<div class="grid-container">

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

## Education {.education .nohead}

```{r}

cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = ifelse(bold == 1, paste0("<span style= 'font-weight: 500'>", what, "</span>"),
                       ifelse(bold == 0, what, NA))) %>%
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what),
         year_end = ifelse(is.na(year_end), '', year_end)
         ) %>% 
  mutate(year = str_c(year_begin, " - ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Research experience {.research .nohead}

```{r}

cv_entries %>% 
  filter(type == 'research') %>% 
  mutate(what = ifelse(bold == 1, paste0("<span style= 'font-weight: 500'>", what, "</span>"),
                       ifelse(bold == 0, what, NA))) %>%
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " - ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

<br class="pageBreak"/>

## Awards & Funding {.award .nohead}

<div class="hangingindent">

```{r}

cv_entries %>%
  filter(type == "award") %>%
  mutate(year_end = ifelse(is.na(year_end), '', paste(' - ', year_end, sep = '')),
         cite = paste0(what, " (", year_begin, year_end, "). ", 
                       ifelse(!is.na(additional_info), 
                              paste0(additional_info, "."),
                              "")
                       )
        ) %>%
  select(cite) %>%
  kable()
```

</div>

## Peer-Reviewed Publications

<div class = "inote">
Icons link to additional content  
</div>

```{r}

make_cite <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL,
                      version = NULL,...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(annual_meeting) {
       conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
      }
    }
    else {
       if(annual_meeting) {
          conference <- paste0("Paper presented at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Paper presented at the ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".") 
      }
    }
  }
  if(!is.null(version)) {
    version <- paste0("R package version ", version, ".")
  }
  authors <- gsub(
    "Anderson, D\\.?",
    "<span style= 'font-weight: 500'>Anderson, D.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, "."),
        version, 
        conference,
        journal, 
        volume,
        book,
        pages, 
        doi,
        place_published)
}

prp <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prp, seq_len(nrow(prp)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prp$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prp$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prp$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prp$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prp$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
#  group_by(year) %>%
#  mutate(count_within_year = 1:n()) %>% 
#  ungroup() %>% 
#  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
#  select(-count_within_year) %>%
  select(-year, -count)

```

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl[1:9, ])
```

</div>

<br class="pageBreak"/>

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl[10:nrow(pubs_tbl), ])
```

</div>


## Manuscripts under review for publication {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "in-review") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 
  
  kable(submitted_tbl) 
}
```

</div>


<br class="pageBreak"/>


## Conference Presentations & Other Talks {.prpa .nohead}

<div class = "hangingindent">

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git)
)
  

conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

kable(conf_tbl[1:7, ])
```

</div>


<br class="pageBreak">

<div class = "hangingindent prpa nohead">

```{r}
kable(conf_tbl[8:18, ])
```

</div>


<br class="pageBreak">

<div class = "hangingindent prpa nohead">

```{r}
kable(conf_tbl[19:28, ])
```

</div>

<br class="pageBreak">

<div class = "hangingindent prpa nohead">

```{r}
kable(conf_tbl[29:nrow(conf_tbl), ])
```

</div>

<div class = "hangingindent submitted nohead">

```{r}
kable(submitted_tbl[4:10, ])
```

</div>

## Teaching {.nohead .tch}

<div class = "inote">
Icons link to additional content  
</div>

```{r}
courses %>% 
  filter(type == "ds") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                         ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""), 
                         credits, " credit hours.",
                         fa_git, fa_web),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()

```

<br class="pageBreak"/>

## Peer review service {.nohead}

I serve on the editorial review board for [Reading Research Quarterly](https://ila.onlinelibrary.wiley.com/journal/19362722) and have served as an ad hoc reviewer for the following journals:

<div class = "adhoc">

```{r}
reviewer <- cv_entries %>%
  filter(type == "peer-reviewer") %>%
  select(what) %>%
  mutate(index = c(rep(1, floor(nrow(.)/2)), 
                   rep(2, nrow(.) - floor(nrow(.)/2))
                   ))


jou1 <- reviewer$what[reviewer$index == 1]
jou2 <- reviewer$what[reviewer$index == 2]

if(length(jou1) < length(jou2)) {
  jou1 <- c(jou1, NA)
}
if(length(jou2) < length(jou1)) {
  jou2 <- c(jou2, NA)
}

data.frame(jou1, jou2) %>%
  kable()
```

</div>

## Additional training (received) {.nohead .extratrain}

<div class = "hangingindent">
```{r}
cv_entries %>% 
  filter(type == "extra-training") %>% 
  mutate(training = paste0(what, " (", year_end, "). ", where, "\\n")) %>% 
  select(training) %>% 
  kable()
```
<div/>

<!-- <br class="pageBreak"> -->

